---
title: "ERD data exploration"
author: "Heather"
date: "11/21/2016"
output: html_document
---
1. Load the libraries, define global objects
```{r echo=FALSE}
library(raster)
library(sp)
library(chron)
library(rgdal)
library(ncdf4)

path_grd='/Volumes/SeaGate/ERD_DOM/ncdf/aspect_filtered.xyz'
x=read.table(path_grd)
coordinates(x)=~V1+V2
template=rasterFromXYZ(x)

path_grd='/Volumes/SeaGate/ERD_DOM/ncdf/aspectnan.xyz'
x=read.table(path_grd)
coordinates(x)=~V1+V2
template_small=rasterFromXYZ(x)  ##use this as template raster for 0.01667 resolution
```

                                      Parent folder: /ncdf/
                                      
                                      
                                      

2. File: aspect_filtered.xyz  (get attributes and plot)

```{r echo=FALSE}
path_grd='/Volumes/SeaGate/ERD_DOM/ncdf/aspect_filtered.xyz'
x=read.table(path_grd)
coordinates(x)=~V1+V2
y=rasterFromXYZ(x)
y
plot(y)
```

3. File: aspectnan.xyz  (get attributes and plot)
```{r echo=FALSE}
path_grd='/Volumes/SeaGate/ERD_DOM/ncdf/aspectnan.xyz'
x=read.table(path_grd)
coordinates(x)=~V1+V2
y=rasterFromXYZ(x)  ##use this as template raster for 0.01667 resolution
y
plot(y)
```

4. File: aviso_delayed_time_madt_h_DATE.nc  (get attributes and plot)
```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/aviso_delayed_time_madt_h_1993-01-01.nc'
nc=nc_open(path_nc)
dname="adt"  ########### change for each netcdf
lon <- ncvar_get(nc, "longitude") # define longitude
nlon <- dim(lon)
lat <- ncvar_get(nc, "latitude", verbose = F) # define latitude
nlat <- dim(lat)
tmp.array <- ncvar_get(nc, dname)
tmp.vec.long <- as.vector(tmp.array)
tmp.mat <- matrix(tmp.vec.long, nrow = nlon * nlat, ncol = 1)
lonlat <- expand.grid(lon, lat)
names(lonlat) <- c("lon","lat")
tmp.df02 <- data.frame(tmp.mat)
tmp.df02 <- cbind(lonlat, tmp.df02)
coordinates(tmp.df02)=~lon+lat
r=rasterize(tmp.df02,template,field="tmp.mat",fun=mean)
nc
r
plot(r)
```

5. File: aviso_delayed_time_madt_u_DATE.nc (get attributes and plot)
A. Variable 1: Geostrophic velocity anomalies: zonal component (eastward water velocity)

```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/aviso_delayed_time_madt_u_1993-01-01.nc'
nc=nc_open(path_nc)
dname="u"  ########### change for each netcdf
lon <- ncvar_get(nc, "longitude") # define longitude
nlon <- dim(lon)
lat <- ncvar_get(nc, "latitude", verbose = F) # define latitude
nlat <- dim(lat)
tmp.array <- ncvar_get(nc, dname)
tmp.vec.long <- as.vector(tmp.array)
tmp.mat <- matrix(tmp.vec.long, nrow = nlon * nlat, ncol = 1)
lonlat <- expand.grid(lon, lat)
names(lonlat) <- c("lon","lat")
tmp.df02 <- data.frame(tmp.mat)
tmp.df02 <- cbind(lonlat, tmp.df02)
coordinates(tmp.df02)=~lon+lat
r=rasterize(tmp.df02,template,field="tmp.mat",fun=mean)
nc
r
plot(r)
```

5. File: aviso_delayed_time_madt_u_DATE.nc (get attributes and plot)
B. Variable 1: Geostrophic velocity anomalies: meridian component (northward water velocity)

```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/aviso_delayed_time_madt_u_1993-01-01.nc'
nc=nc_open(path_nc)
dname="v"  ########### change for each netcdf
lon <- ncvar_get(nc, "longitude") # define longitude
nlon <- dim(lon)
lat <- ncvar_get(nc, "latitude", verbose = F) # define latitude
nlat <- dim(lat)
tmp.array <- ncvar_get(nc, dname)
tmp.vec.long <- as.vector(tmp.array)
tmp.mat <- matrix(tmp.vec.long, nrow = nlon * nlat, ncol = 1)
lonlat <- expand.grid(lon, lat)
names(lonlat) <- c("lon","lat")
tmp.df02 <- data.frame(tmp.mat)
tmp.df02 <- cbind(lonlat, tmp.df02)
coordinates(tmp.df02)=~lon+lat
r=rasterize(tmp.df02,template,field="tmp.mat",fun=mean)
nc
r
plot(r)
```

6. File: bathyrms.xyz (get attributes and plot)

```{r echo=FALSE}
path_grd='/Volumes/SeaGate/ERD_DOM/ncdf/bathyrms.xyz'
x=read.table(path_grd)
coordinates(x)=~V1+V2
y=rasterFromXYZ(x)
y
plot(y)
```

7. File: bathyrms_blockmean.xyz (get attributes and plot)
##### Keep working on this one. I think it's slope, aspect, rms, depth, others??

```{r echo=FALSE}
path_grd='/Volumes/SeaGate/ERD_DOM/ncdf/bathyrms_blockmean.xyz'
x=read.table(path_grd)
coordinates(x)=~V1+V2
a=rasterize(x,template_small,field="V3",fun=mean)  ## irregular grid, have to switch it up
a
plot(a)
#b=raster('/Volumes/SeaGate/ERD_DOM/ncdf/bathyrms_blockmean.xyz',varname="V3")
```

8. File: etopo180_48d2_23d2_fc23.nc (get attributes and plot)
(Bathymetry)

```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/Bight/etopo180_48d2_23d2_fc23.nc'
nc=nc_open(path_nc)
b=raster('/Volumes/SeaGate/ERD_DOM/ncdf/Bight/etopo180_48d2_23d2_fc23.nc',varname="altitude")
nc
b
plot(b)
```

9. File: jplG1SST_DATE.nc (get attributes and plot)
(Analysed Sea Surface Temperature, 1km SST blended from 8 satellite observations (GHRSST))

```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/Bight/jplG1SST_2012-01-01.nc'
nc=nc_open(path_nc)
dname="SST"  ########### change for each netcdf
b=raster(path_nc,varname="SST")
nc
b
plot(b)
```

10. File: nodcPH2sstd1day_DATE.nc (get attributes and plot)
(Sea Surface Temperature, skin only, AVHRR)

```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/Bight/nodcPH2sstd1day_1990-05-01.nc'
nc=nc_open(path_nc)
dname="sea_surface_temperature"  ########### change for each netcdf
lon <- ncvar_get(nc, "longitude") # define longitude
nlon <- dim(lon)
lat <- ncvar_get(nc, "latitude", verbose = F) # define latitude
nlat <- dim(lat)
tmp.array <- ncvar_get(nc, dname)
tmp.vec.long <- as.vector(tmp.array)
tmp.mat <- matrix(tmp.vec.long, nrow = nlon * nlat, ncol = 1)
lonlat <- expand.grid(lon, lat)
names(lonlat) <- c("lon","lat")
tmp.df02 <- data.frame(tmp.mat)
tmp.df02 <- cbind(lonlat, tmp.df02)
coordinates(tmp.df02)=~lon+lat
template2=raster()
res(template2)=0.0417
ncol(template2)=nlon
nrow(template2)=nlat
xmin(template2)=-120.97917175293
xmax(template2)=-115.97917175293
ymin(template2)=29.9791717529297
ymax(template2)=34.9791717529297
r=rasterize(tmp.df02,template2,field="tmp.mat",fun=mean)
nc
r
plot(r)
```

11. File: etopo-bight-sd.nc (get attributes and plot)
(Standard deviation of topography, calculated over space using a 3x3 roving window)

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/Bight/sd/etopo-bight-sd.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="layer")
nc
r
plot(r)
```

12. File: jplG1-sd-2012-01-01.nc (get attributes and plot)
(standard deviation of GHRSST, 3x3 roving window) ##this layer comes in upside, need to flip (same as 13 below, but at finer resolution (0.009980044))

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/Bight/sd/jplG1-sd-2012-01-01.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="layer")
nc
r
plot(r)
```

13. File: jplG1-sd-regrid2012-01-01.nc (get attributes and plot)
(standard deviation of GHRSST, 3x3 roving window) ## same as above (12) but at 0.01666667 resolution

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/Bight/sd/jplG1-sd-regrid2012-01-01.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="layer")
nc
r
plot(r)
```

14. File: nodcPH2-sd-1990-01-01.nc (get attributes and plot)
standard deviation...of what? look up..  RESOLUTION: 0.04132231

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/Bight/sd/nodcPH2-sd-1990-01-01.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="layer")
nc
r
plot(r)
```

15. File: nodcPH2-sd-regrid1990-01-01.nc (get attributes and plot)
standard deviation...of what? look up..  RESOLUTION: 0.01666667 (same as above but finer)

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/Bight/sd/nodcPH2-sd-regrid1990-01-01.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="layer")
nc
r
plot(r)
```

16. File: depth_filtered.xyz (get attributes and plot)
Depth at res of 0.25 - - find source

```{r echo=FALSE}
path_grd="/Volumes/SeaGate/ERD_DOM/ncdf/depth_filtered.xyz"
x=read.table(path_grd)
coordinates(x)=~V1+V2
y=rasterFromXYZ(x)
y
plot(y)
```

17. File: depth.xyz (get attributes and plot)
Depth at res of 0.01667 - - find source

```{r echo=FALSE}
path_grd="/Volumes/SeaGate/ERD_DOM/ncdf/depth.xyz"
x=read.table(path_grd)
coordinates(x)=~V1+V2
y=rasterFromXYZ(x)
y
plot(y)
```

18. File: depthnan.xyz (get attributes and plot)
Depth at res of 0.01667 - - find source, SAME AS ABOVE I BELIEVE

```{r echo=FALSE}
path_grd="/Volumes/SeaGate/ERD_DOM/ncdf/depth.xyz"
x=read.table(path_grd)
coordinates(x)=~V1+V2
y=rasterFromXYZ(x)
y
plot(y)
```

19. File: erdMBchla8day_2013-10-12.nc (get attributes and plot)
RESOLUTION: 0.01666667, MODIS CHLA, need to flip

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/erdMBchla8day_2013-10-12.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="chlorophyll")
nc
r
plot(r)
```

20. File: erdPHssta8day_1981-09-02.nc (get attributes and plot)
RESOLUTION: 0.04394531, pathfinder SST

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/erdPHssta8day_1981-09-02.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="sst")
nc
r
plot(r)
```

21. File: erdSHchla8day_1998-01-05.nc (get attributes and plot)
RESOLUTION: 0.0125, SeaWiFS chla (Chlorophyll-a, Orbview-2 SeaWiFS, 0.0125°, West US (8 Day Composite))

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/erdSHchla8day_1998-01-05.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="chlorophyll")
nc
r
plot(r)
```

22. File: erdSWchla8day_1997-09-02.nc (get attributes and plot)
RESOLUTION: 0.08335263, SeaWiFS chla (Chlorophyll-a, Orbview-2 SeaWiFS, Global (8 Day Composite))

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/erdSWchla8day_1997-09-02.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="chlorophyll")
nc
r
plot(r)
```

23. File: etopo360.nc (get attributes and plot)
RESOLUTION: 0.0166667 degrees, Topography, ETOPO1, 0.0166667 degrees, Global (longitude 0 to 360), (Ice Sheet Surface)

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/etopo360.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="altitude")
nc
r
plot(r)
```

24. File: jplL4AvhrrOIv1fv2_1981-09-01.nc (get attributes and plot)
GHRSST Level 4 AVHRR_OI Global Blended Sea Surface Temperature Analysis, Global, 0.25 Degree, Daily

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/jplL4AvhrrOIv1fv2_1981-09-01.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="analysed_sst")
nc
r
plot(r)
```

25. File: ncdcOwDly_1987-07-09.nc (get attributes and plot)
NOAA/NCDC Blended Daily 0.25-degree Sea Surface Winds

```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf/ncdcOwDly_2000-07-09.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="v")
nc
r
plot(r)
```

26. File: sd_blockmean.xyz (get attributes and plot)
Depth at res of 0.01667 - - find source, possibly standard deviation but values look like depth values

```{r echo=FALSE}
path_grd="/Volumes/SeaGate/ERD_DOM/ncdf/sd_blockmean.xyz"
x=read.table(path_grd)
coordinates(x)=~V1+V2
res(template_small)=0.01667
a=rasterize(x,template_small,field="V3",fun=mean)  ## irregular grid, have to switch it up
a
plot(a)
```

27. File: slope_filtered.xyz (get attributes and plot)
Slope at res of 0.25 - - find source

```{r echo=FALSE}
path_grd="/Volumes/SeaGate/ERD_DOM/ncdf/slope_filtered.xyz"
x=read.table(path_grd)
coordinates(x)=~V1+V2
y=rasterFromXYZ(x)
y
plot(y)
```

28. File: slopenan.xyz (get attributes and plot)
Slope at res of 0.01667 - - find source, same as above but with finer resolution

```{r echo=FALSE}
path_grd="/Volumes/SeaGate/ERD_DOM/ncdf/slopenan.xyz"
x=read.table(path_grd)
coordinates(x)=~V1+V2
y=rasterFromXYZ(x)
y
plot(y)
```



                                      Parent folder: /ncdf_2015/
                                      
                                      
29. File: dt_global_allsat_madt_h_20150101_20150914.nc (get attributes and plot)
Delayed-Time Level-4 sea surface height above Geoid products from multi-satellite observations.
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/dt_global_allsat_madt_h_20150101_20150914.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="adt")
nc
r
plot(r)
```

30. File: dt_global_allsat_madt_uv_20150101_20150914.nc (get attributes and plot)
DT merged all satellites Global Ocean Gridded Absolute Geostrophic Velocities L4 product - surface_eastward_geostrophic_sea_water_velocity
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/dt_global_allsat_madt_uv_20150101_20150914.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="u")
nc
r
plot(r)
```

31. File: dt_global_allsat_madt_uv_20150101_20150914.nc (get attributes and plot)
DT merged all satellites Global Ocean Gridded Absolute Geostrophic Velocities L4 product - surface_northward_geostrophic_sea_water_velocity
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/dt_global_allsat_madt_uv_20150101_20150914.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="v")
nc
r
plot(r)
```

32. File: dt_global_allsat_msla_h_20150101_20150914.nc (get attributes and plot)
Delayed-Time Level-4 sea surface height above Mean Sea Surface products from multi-satellite observations.
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/dt_global_allsat_msla_h_20150101_20150914.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="sla")
nc
r
plot(r)
```

33. File: erdMBchla8day_2015-01-01.nc (get attributes and plot)
Chlorophyll-a, Aqua MODIS, NPP, 0.025 degrees, Pacific Ocean, EXPERIMENTAL (8 Day Composite)
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/erdMBchla8day_2015-01-01.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="chlorophyll")
nc
r
plot(r)
```

34. File: jplG1SST_2015-01-01.nc (get attributes and plot)
GHRSST Global 1-km Sea Surface Temperature (G1SST), Global, 0.01 Degree, Daily
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/jplG1SST_2015-01-01.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="SST")
nc
r
plot(r)
```

35. File: jplL4AvhrrOIv1fv2_2015-01-01.nc (get attributes and plot)
GHRSST Level 4 AVHRR_OI Global Blended Sea Surface Temperature Analysis, Global, 0.25 Degree, Daily
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/jplL4AvhrrOIv1fv2_2015-01-01.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="analysed_sst")
nc
r
plot(r)
```

36. File: ncdcOwDly_2015-01-09.nc (get attributes and plot)
NOAA/NCDC Blended Daily 0.25-degree Sea Surface Winds
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/ncdcOwDly_2015-01-09.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="v")
nc
r
plot(r)
```



                                      Parent folder: /FSLE/
                                      
                                      
29. File: dt_global_allsat_madt_fsle_20150907_20160414.nc (get attributes and plot)
This dataset contains Backward-in-time FSLE product deduced from DT merged Global Ocean Gridded Absolute Geostrophic Velocities SSALTO/Duacs L4 product (version 2014) (FSLEs based on the maximum eigenvalue of the Cauchy-Green strain tensor)
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/FSLE/dt_global_allsat_madt_fsle_20150907_20160414.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="fsle_max")
nc
r
plot(r)
```


