---
title: "ERD data exploration"
author: "Heather"
date: "11/21/2016"
output: html_document
---
Load the libraries, define global objects
```{r echo=FALSE}
library(raster)
library(sp)
library(chron)
library(rgdal)
library(ncdf4)

path_grd='/Volumes/SeaGate/ERD_DOM/ncdf/aspect_filtered.xyz'
x=read.table(path_grd)
coordinates(x)=~V1+V2
template=rasterFromXYZ(x)

path_grd='/Volumes/SeaGate/ERD_DOM/ncdf/aspectnan.xyz'
x=read.table(path_grd)
coordinates(x)=~V1+V2
template_small=rasterFromXYZ(x)  ##use this as template raster for 0.01667 resolution
```

                                      Parent folder: /ncdf/
                                      

1(4.) File: aviso_delayed_time_madt_h_DATE.nc  (get attributes and plot)
```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/aviso_delayed_time_madt_h_1993-01-01.nc'
nc=nc_open(path_nc)
dname="adt"  ########### change for each netcdf
lon <- ncvar_get(nc, "longitude") # define longitude
nlon <- dim(lon)
lat <- ncvar_get(nc, "latitude", verbose = F) # define latitude
nlat <- dim(lat)
tmp.array <- ncvar_get(nc, dname)
tmp.vec.long <- as.vector(tmp.array)
tmp.mat <- matrix(tmp.vec.long, nrow = nlon * nlat, ncol = 1)
lonlat <- expand.grid(lon, lat)
names(lonlat) <- c("lon","lat")
tmp.df02 <- data.frame(tmp.mat)
tmp.df02 <- cbind(lonlat, tmp.df02)
coordinates(tmp.df02)=~lon+lat
r=rasterize(tmp.df02,template,field="tmp.mat",fun=mean)
nc
r
plot(r)
```

2(5.) File: aviso_delayed_time_madt_u_DATE.nc (get attributes and plot)
A. Variable 1: Geostrophic velocity anomalies: zonal component (eastward water velocity)

```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/aviso_delayed_time_madt_u_1993-01-01.nc'
nc=nc_open(path_nc)
dname="u"  ########### change for each netcdf
lon <- ncvar_get(nc, "longitude") # define longitude
nlon <- dim(lon)
lat <- ncvar_get(nc, "latitude", verbose = F) # define latitude
nlat <- dim(lat)
tmp.array <- ncvar_get(nc, dname)
tmp.vec.long <- as.vector(tmp.array)
tmp.mat <- matrix(tmp.vec.long, nrow = nlon * nlat, ncol = 1)
lonlat <- expand.grid(lon, lat)
names(lonlat) <- c("lon","lat")
tmp.df02 <- data.frame(tmp.mat)
tmp.df02 <- cbind(lonlat, tmp.df02)
coordinates(tmp.df02)=~lon+lat
r=rasterize(tmp.df02,template,field="tmp.mat",fun=mean)
nc
r
plot(r)
```

3(5.) File: aviso_delayed_time_madt_u_DATE.nc (get attributes and plot)
B. Variable 1: Geostrophic velocity anomalies: meridian component (northward water velocity)

```{r echo=FALSE}
path_nc='/Volumes/SeaGate/ERD_DOM/ncdf/aviso_delayed_time_madt_u_1993-01-01.nc'
nc=nc_open(path_nc)
dname="v"  ########### change for each netcdf
lon <- ncvar_get(nc, "longitude") # define longitude
nlon <- dim(lon)
lat <- ncvar_get(nc, "latitude", verbose = F) # define latitude
nlat <- dim(lat)
tmp.array <- ncvar_get(nc, dname)
tmp.vec.long <- as.vector(tmp.array)
tmp.mat <- matrix(tmp.vec.long, nrow = nlon * nlat, ncol = 1)
lonlat <- expand.grid(lon, lat)
names(lonlat) <- c("lon","lat")
tmp.df02 <- data.frame(tmp.mat)
tmp.df02 <- cbind(lonlat, tmp.df02)
coordinates(tmp.df02)=~lon+lat
r=rasterize(tmp.df02,template,field="tmp.mat",fun=mean)
nc
r
plot(r)
```

                                      Parent folder: /ncdf_2015/
                                      
                                      
4(29.) File: dt_global_allsat_madt_h_20150101_20150914.nc (get attributes and plot)
Delayed-Time Level-4 sea surface height above Geoid products from multi-satellite observations.
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/dt_global_allsat_madt_h_20150101_20150914.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="adt")
nc
r
plot(r)
```

5(30.) File: dt_global_allsat_madt_uv_20150101_20150914.nc (get attributes and plot)
DT merged all satellites Global Ocean Gridded Absolute Geostrophic Velocities L4 product - surface_eastward_geostrophic_sea_water_velocity
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/dt_global_allsat_madt_uv_20150101_20150914.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="u")
nc
r
plot(r)
```

6(31.) File: dt_global_allsat_madt_uv_20150101_20150914.nc (get attributes and plot)
DT merged all satellites Global Ocean Gridded Absolute Geostrophic Velocities L4 product - surface_northward_geostrophic_sea_water_velocity
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/dt_global_allsat_madt_uv_20150101_20150914.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="v")
nc
r
plot(r)
```

7(32.) File: dt_global_allsat_msla_h_20150101_20150914.nc (get attributes and plot)
Delayed-Time Level-4 sea surface height above Mean Sea Surface products from multi-satellite observations.
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_2015/dt_global_allsat_msla_h_20150101_20150914.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="sla")
nc
r
plot(r)
```


                                             Parent folder: /ncdf_ADD/AVISOraw
8() File: dt_global_allsat_msla_h_19930101_20140106.nc (get attributes and plot)
DT merged Global Ocean Gridded Sea Level Anomalies SSALTO/Duacs L4 product
```{r echo=FALSE}
pathnc="/Volumes/SeaGate/ERD_DOM/ncdf_ADD/AVISOraw/all-sat-DRT/h/1993/dt_global_allsat_msla_h_19930101_20140106.nc"
nc=nc_open(pathnc)
r=raster(pathnc,varname="sla")
nc
r
plot(r)
```
 